\subsection{What is the concept of monitoring and how is it used in general?}
\label{subsec:ConceptMonitoring}

Monitoring is getting popular nowadays. It is known as a process which is managing, observing and intervening into other processes or systems.\cite{Jammes2012} Its main goal is to control the actions, as well as prevent and fix failures.\cite{Dinu2011} Monitoring can be used in different ways, based on the Use-Case field and environment.\cite{Dinu2011} The most common areas of use nowadays, next to distributed systems,\cite{Jammes2012} is the medical field. Operations, hearth disease and blood pressure are continuously getting monitored, to either prevent failures or help patiences in need. This technique gives a range of security and control, which could not be given by any person for distributed systems.\cite{Jammes2012}
\\
 In \isds, the core aim of monitoring is to fix and prevent faults quickly. This improves the quality of the system and its capabilities. Monitoring applications are usually integrated into the structure of communication in between the distributed systems.\cite{Jammes2012} By virus or dangerous information which might get send from one computer to an another, monitoring would intervene and stop or divorce the machine from the whole system, to save the systems health. Industries nowadays are facing the problem, of increasing complexities in technique and systems that they are using.\cite{Jammes2012} To find and fix failures in such situation, monitoring is very useful. It identifies failures much efficiently as a person could possibly do.\cite{Jammes2012}
 
 %TODO: Include range of usecases. especially log collection vs. uptime report / usage / load 